% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{class-board}{%
\section{Class Board}\label{class-board}}

The Board class extends the JPanel class, and it represents the
Minesweeper board. The board consists of cells, some of which contain
mines. The objective of the game is to uncover all cells that do not
contain mines without detonating any of the cells that do contain mines.

\hypertarget{attributes}{%
\section{Attributes}\label{attributes}}

\begin{itemize}
\tightlist
\item
  NUM\_IMAGES: A constant integer representing the number of images
  available for the cells on the board.
\item
  CELL\_SIZE: A constant integer representing the size of each cell on
  the board.
\item
  COVER\_FOR\_CELL: A constant integer representing the value assigned
  to a cell that is covered.
\item
  MARK\_FOR\_CELL: A constant integer representing the value assigned to
  a cell that has been marked with a flag.
\item
  EMPTY\_CELL: A constant integer representing the value assigned to a
  cell that is not covered and does not contain a mine.
\item
  MINE\_CELL: A constant integer representing the value assigned to a
  cell that contains a mine.
\item
  COVERED\_MINE\_CELL: A constant integer representing the value
  assigned to a cell that contains a mine and is covered.
\item
  MARKED\_MINE\_CELL: A constant integer representing the value assigned
  to a cell that contains a mine and has been marked with a flag.
\item
  DRAW\_MINE: A constant integer representing the index of the image
  that represents a mine.
\item
  DRAW\_COVER: A constant integer representing the index of the image
  that represents a covered cell.
\item
  DRAW\_MARK: A constant integer representing the index of the image
  that represents a cell that has been marked with a flag.
\item
  DRAW\_WRONG\_MARK: A constant integer representing the index of the
  image that represents a cell that has been marked with a flag but does
  not contain a mine.
\item
  field: An integer array that represents the state of each cell on the
  board. The value assigned to each cell is determined by the constants
  described above.
\item
  inGame: A boolean value that represents whether the game is currently
  in progress.
\item
  mines\_left: An integer representing the number of mines that have not
  been marked with a flag.
\item
  img: An array of Image objects representing the images that can be
  displayed on the cells.
\item
  mines: An integer representing the number of mines on the board.
\item
  rows: An integer representing the number of rows on the board.
\item
  cols: An integer representing the number of columns on the board.
\item
  all\_cells: An integer representing the total number of cells on the
  board.
\item
  statusbar: A JLabel object representing the status bar at the bottom
  of the game window.
\end{itemize}

\hypertarget{constructor}{%
\subsection{Constructor}\label{constructor}}

\hypertarget{public-boardjlabel-statusbar}{%
\subsubsection{public Board(JLabel
statusbar)}\label{public-boardjlabel-statusbar}}

The constructor creates a new Board object and sets the statusbar field
to the specified JLabel object. It initializes the img field by loading
the images from the ``images'' directory. It sets the double buffer of
the panel to true, adds a MouseListener to the panel, and calls the
newGame() method to start a new game.

\hypertarget{methods}{%
\subsection{Methods}\label{methods}}

\hypertarget{public-void-newgame}{%
\subsubsection{public void newGame()}\label{public-void-newgame}}

This method starts a new game by initializing the field array to contain
only covered cells, setting the inGame flag to true, and setting the
number of mines left to the total number of mines. It then randomly
places the specified number of mines on the board and updates the values
of the cells surrounding the mines to indicate the number of mines in
the adjacent cells. private void find\_empty\_cells(int j)

This method is called when a cell that does not contain a mine is
uncovered. It recursively uncovers all adjacent cells that do not
contain mines. The parameter j is the index of the current cell in the

\hypertarget{public-void-paint}{%
\subsection{public void paint}\label{public-void-paint}}

The \texttt{paint} method is responsible for painting the Board in the
window. The code is divided into three parts: covering the cells with an
image that hides the content, displaying the content of a cell according
to the value in the field array, and displaying the game status
(win/lose).

\hypertarget{mouseadapter}{%
\section{MouseAdapter}\label{mouseadapter}}

\texttt{MouseAdapter} is a convenience class that implements the
\texttt{MouseListener} interface. The \texttt{MouseListener} interface
is used to receive mouse events. This class has empty implementations
for all methods defined in the \texttt{MouseListener} interface.

The \texttt{MinesAdapter} class is an inner class of the \texttt{Board}
class and is used to handle mouse events. This class overrides the
\texttt{mousePressed} method to handle left and right mouse clicks.
Left-clicking on a covered cell will uncover the cell, and
right-clicking on a covered cell will mark the cell with a flag.
Left-clicking on an uncovered cell will reveal its content, and
right-clicking on an uncovered cell will remove the flag. The method
also checks the game status and updates the game accordingly.

\end{document}
